### 2018-09-13 post-linearity-2018/reviews-and-responses.txt

# Linearity Paper Final Version Revision

May 22, 2018

## -------------------- Review 1 --------------------
PAPER: 3
TITLE: On the Lambek Calculus with an Exchange Modality AUTHORS: Jiaming Jiang, Harley Eades Iii and Valeria de Paiva
Overall evaluation: 1 (weak accept)
----------- Overall evaluation -----------

This paper introduces a type system for (non-symmetric) monoidal
adjunctions between a symmetric monoidal closed category and a
monoidal bi-closed category called CNC logic. It can be considered as
a variant of Benton's LNL logic for symmetric monoidal adjunctions
between a cartesian closed category and a symmetric monoidal closed
category.  This paper is in general clearly written and should be easy
to follow for readers familiar with the categorical models of linear
logic. I did not check the detail of CNC logic (largely because there
is no information on its equational or rewriting theory). However,
since it is based on well-established categorical structures, I
believe that there should be no substantial errors.  My knowledge on
the Lambek Calculus is rather limited, but I think that having a good
categorical semantics and type system for Lambek Calculus should be
useful and makes a good case of technology-transfer from Linear Logic
to the Lambek Calculus. Thus I recommend acceptance.

- Lemma 7:

I think that this result was already in Kock's 1970 original paper.

- Corollary 11:

I think that the statement of this corollary is wrong. As Benton (and
many other people) points out, the category of coalgebras of a linear
exponential comonad on a symmetric monoidal closed category does not
have to be cartesian closed (and we should take some subcategory
instead). The same applies to the setting of this paper.

- Theorem 18:

I am not sure what "a complete moel" means - completeness
w.r.t. derivablity or w.r.t. equational theory? (It seems that the
same question applies to [8].)

- Section 4:

I agree that the Dialectica categories developped here are
interesting, but also wonder if some much easier models could also do
the good job without much technical complication.  For instance,
starting with a strong monoidal functor F:C->D from a symmetric
monoidal category C to a monoidal category D, the monoidal
cocompletion (i.e. taking the presheaf categories) immediately gives
an LAM [C^op,Set] -> [D^op.Set], thus a sound model of CNC logic.

- A work which might be related to this paper is

Masahito Hasegawa:

Linear Exponential Comonads without Symmetry. LINEARITY 2016: 54-63
where the author axiomatizes comonads corresponding to monoidal
adjunctions between a cartesian category and a monoidal category. It
might be interesting to do the same for LAM (which should be something
like "linear exchange comonads").

- On the direction of arrows:

It seems that the direction of arrow types is not in harmony with the
standard Lambek Calculus nor with the usual convention for internal
homs in monoidal bi-closed categories. Is there any reason for this
choice?

### Response to Review 1:
* Will add the reference by Hasegawa.

* Lemma 7

Only found half of it is in Kock's 1970 paper. The full if and only if
version is in Kock's 1972 paper.  As said at the beginning of the 1972
paper: "In [4] (i.e., *Monads on Symmetric Monoidal Closed
Categories*) we proved that a commutative monad on a symmetric
monoidal closed category carries the structure of a symmetric monoidal
monad ([4], Theorem 3.2). We here prove the converse, so that, taken
together, we have: there is a 1-1 correspondence between commutative
monads and symmetric monoidal monads (Theorem 2.3 below)."

**Have added the reference and changed the citation for Lemma 7.**
* Corollary 11

The reviewer thought we were trying to prove that it is cartesian
closed.  The reviewer writes "As Benton (and many other people) points
out, the category of coalgebras of a linear exponential comonad on a
symmetric monoidal closed category does not have to be cartesian
closed (and we should take some subcategory instead)."

HDE: They are actually correct, and it is about closure rather than
carteisan.  I reworded the corollary to be more precise.

**Didn't change anything**
* Theorem 18
The reviewer is not sure what "complete" means.
**Added "(w.r.t. derivability and quational theory)"**
* Direction of Arrows
Not sure why the reviewer thinks the direction of arrows is
wrong. Wikipedia on closed monoidal category uses $\Rightarrow$ for
right adjoint and $\Leftarrow$ for left adjoint. The original Lambek
paper uses \ and /. The page on closed monoidal cateogry in nLab
(https://ncatlab.org/nlab/show/closed+monoidal+category) uses square
brackets, i.e., $[b,c]$ for $b\Rightarrow c$.
**Didn't change anything**

## ----------------------- Review 2 ---------------------
PAPER: 3
TITLE: On the Lambek Calculus with an Exchange Modality AUTHORS: Jiaming Jiang, Harley Eades Iii and Valeria de Paiva
Overall evaluation: 2 (accept)
----------- Overall evaluation -----------

The paper seems as a good contribution to the development of the
research in Lambek Calculus and its extensions and in Non Commutative
Linear Logic. The results seem accurate and well presented. The
authors have a very good experience in this field. It would be
interesting to compare this work with Non Commutative Logic introduced
by Abrusci and Ruet.

### Response to Review 2
* Reference by Abrusci and Ruet:
**Will add the reference.**

### 2018-09-13 reviews-and-responses.txt

# Linearity Paper Final Version Revision

May 22, 2018

## -------------------- Review 1 --------------------
PAPER: 3
TITLE: On the Lambek Calculus with an Exchange Modality AUTHORS: Jiaming Jiang, Harley Eades Iii and Valeria de Paiva
Overall evaluation: 1 (weak accept)
----------- Overall evaluation -----------
This paper introduces a type system for (non-symmetric) monoidal adjunctions between a symmetric monoidal closed category and a monoidal bi-closed category called CNC logic. It can be considered as a variant of Benton's LNL logic for symmetric monoidal adjunctions between a cartesian closed category and a symmetric monoidal closed category.
This paper is in general clearly written and should be easy to follow for readers familiar with the categorical models of linear logic. I did not check the detail
of CNC logic (largely because there is no information on its equational or rewriting theory). However, since it is based on well-established categorical structures, I believe that there should be no substantial errors.
My knowledge on the Lambek Calculus is rather limited, but I think that having a good categorical semantics and type system for Lambek Calculus should be useful and makes a good case of technology-transfer from Linear Logic to the Lambek Calculus. Thus I recommend acceptance.
- Lemma 7:
I think that this result was already in Kock's 1970 original paper.
- Corollary 11:
I think that the statement of this corollary is wrong. As Benton (and many other people) points out, the category of coalgebras of a linear exponential comonad on a symmetric monoidal closed category does not have to be cartesian closed (and we should take some subcategory instead). The same applies to the setting of this paper.
- Theorem 18:
I am not sure what "a complete moel" means - completeness w.r.t. derivablity or w.r.t. equational theory? (It seems that the same question applies to
[8].)
- Section 4:
I agree that the Dialectica categories developped here are interesting,
but also wonder if some much easier models could also do the good job without
much technical complication.
For instance, starting with a strong monoidal functor F:C->D from a symmetric monoidal category C to a monoidal category D, the monoidal cocompletion (i.e. taking the presheaf categories) immediately gives an LAM [C^op,Set] -> [D^op.Set], thus
a sound model of CNC logic.
- A work which might be related to this paper is
Masahito Hasegawa:
Linear Exponential Comonads without Symmetry. LINEARITY 2016: 54-63
where the author axiomatizes comonads corresponding to monoidal adjunctions between a cartesian category and a monoidal category. It might be interesting
to do the same for LAM (which should be something like "linear exchange comonads").
- On the direction of arrows:
It seems that the direction of arrow types is not in harmony with the standard Lambek Calculus nor with the usual convention for internal homs in monoidal bi-closed categories. Is there any reason for this choice?

### Response to Review 1:
* Will add the reference by Hasegawa. 
* Lemma 7
Only found half of it is in Kock's 1970 paper. The full if and only if version is in Kock's 1972 paper.
As said at the beginning of the 1972 paper: "In [4] (i.e., *Monads on Symmetric Monoidal Closed Categories*) we proved that a commutative monad on a symmetric monoidal closed category carries the structure of a symmetric monoidal monad ([4], Theorem 3.2). We here prove the converse, so that, taken together, we have: there is a 1-1 correspondence between commutative monads and symmetric monoidal monads (Theorem 2.3 below)."
**Have added the reference and changed the citation for Lemma 7.**
* Corollary 11
The reviewer thought we were trying to prove that it is cartesian closed.
The reviewer writes "As Benton (and many other people) points out, the category of coalgebras of a linear exponential comonad on a symmetric monoidal closed category does not have to be cartesian closed (and we should take some subcategory instead)."
**Didn't change anything**
* Theorem 18
The reviewer is not sure what "complete" means.
**Added "(w.r.t. derivability and quational theory)"**
* Direction of Arrows
Not sure why the reviewer thinks the direction of arrows is wrong. Wikipedia on closed monoidal category uses $\Rightarrow$ for right adjoint and $\Leftarrow$ for left adjoint. The original Lambek paper uses \ and /. The page on closed monoidal cateogry in nLab (https://ncatlab.org/nlab/show/closed+monoidal+category) uses square brackets, i.e., $[b,c]$ for $b\Rightarrow c$.
**Didn't change anything**

## ----------------------- Review 2 ---------------------
PAPER: 3
TITLE: On the Lambek Calculus with an Exchange Modality AUTHORS: Jiaming Jiang, Harley Eades Iii and Valeria de Paiva
Overall evaluation: 2 (accept)
----------- Overall evaluation -----------
The paper seems as a good contribution to the development of the research in Lambek Calculus and its extensions and in Non Commutative Linear Logic. The results seem accurate and well presented. The authors have a very good experience in this field. It would be interesting to compare this work with Non Commutative Logic introduced by Abrusci and Ruet.

### 2018-09-13 post-linearity-2018/adjoint-models.tex
Uncompilable Post Proceeding for Linearity

\begin{corollary}
  The co-Eilenberg-Moore category $\cat{L}^{FG}$ of $FG : \cat{L} \mto
  \cat{L}$ is symmetric monoidal closed.
\end{corollary}
\begin{proof}
  The proof that $\cat{L}^{FG}$ is monoidal closed follows similarly
  to Benton~\cite{Benton:1994}.
\end{proof}

>>>>

\begin{corollary}
  The subcategory, $\mathsf{Exp}(\cat{L}^{FG})$, of the
  co-Eilenberg-Moore category $\cat{L}^{FG}$ consisting of the free
  exponential coalgebras is symmetric monoidal closed.
\end{corollary}
\begin{proof}
  The proof that $\mathsf{Exp}(\cat{L}^{FG})$ is monoidal closed
  follows similarly to Benton~\cite{Benton:1994}.
\end{proof}

### 2018-09-13 post-linearity-2018/fwork.tex
Uncompilable Post Proceeding for Linearity

>>>>

Hasegawa~\cite{EPTCS238.6} studies the linear of-course modality,
$!A$, as a comonad induced by an adjunction between a cartesian closed
category a (non-symmetric) monoidal category.  The results here
generalizes his by generalizing the cartesian closed category to a
symmetric monoidal closed category.  However, his approach focuses on
the comonad rather than the adjunctions.  It would be interesting to
do the same for LAM as well.

### 2018-09-13 post-linearity-2018/sequent.tex
Uncompilable Post Proceeding for Linearity

We now introduce Commutative/Non-commutative (CNC) logic in the form
of a term assignment.  One should view this logic as composed of two
logics; one sitting to the left of the other.  On the left, there is
intuitionistic linear logic, denoted by $\cat{C}$, and on the right is
the Lambek calculus denoted by $\cat{L}$.  Then we connect these two
systems by a pair of monoidal adjoint functors $\cat{C} : \func{F}
\dashv \func{G} : \cat{L}$.  Keeping this intuition in mind we now
define the syntax for CNC logic.
\begin{definition}
  \label{def:Lambek-syntax}
  The following grammar describes the syntax of CNC logic:
  \begin{center}\vspace{-3px}\small
    \begin{math}
      \begin{array}{lll}        
        \text{($\cat{C}$-Types)} & [[W]],[[X]],[[Y]],[[Z]] ::= [[UnitT]] \mid [[X (*) Y]] \mid [[X -o Y]] \mid [[Gf A]]\\
        \text{($\cat{L}$-Types)} & [[A]],[[B]],[[C]],[[DT]] ::= [[UnitS]] \mid [[A (>) B]] \mid [[A -> B]] \mid [[B <- A]] \mid [[F X]]\\        
        \text{($\cat{C}$-Terms)} & [[t]] ::= [[x]] \mid [[trivT]] \mid [[t1 (*) t2]] \mid [[let t1 : X be q in t2]] \mid [[\x:X.t]] \mid [[t1 t2]] \mid [[ex t1 , t2 with x1 , x2 in t3]] \mid [[Gf s]]\\
        \text{($\cat{L}$-Terms)} & [[s]] ::= [[x]] \mid [[trivS]] \mid [[s1 (>) s2]] \mid [[let s1 : A be p in s2]] \mid [[let t : X be q in s]] \mid [[\l x : A.s]] \mid [[\r x : A . s]] \\
        & \,\,\,\,\,\,\,\,\,\mid [[appl s1 s2]] \mid [[appr s1 s2]] \mid [[F t]]\\        
        \text{($\cat{C}$-Patterns)} & [[q]] ::= [[trivTp]] \mid [[x]] \mid [[q1 (*) q2]] \mid [[Gf p]]\\
        \text{($\cat{L}$-Patterns)} & [[p]] ::= [[trivSp]] \mid [[x]] \mid [[p1 (>) p2]] \mid [[F q]]\\        
        \text{($\cat{C}$-Contexts)} & [[I]],[[P]] ::= [[.]] \mid [[x : X]] \mid [[I,P]]\\
        \text{($\cat{L}$-Contexts)} & [[G]],[[D]] ::= [[.]] \mid [[x : A]] \mid [[x : X]] \mid [[G;D]]\\        
        \text{($\cat{C}$-Typing Judgment)} & [[I |-c t : X]]\\
        \text{($\cat{L}$-Typing Judgment)} & [[G |-l s : A]]\\
      \end{array}
    \end{math}
  \end{center}
\end{definition}

The syntax for $\cat{C}$-types are the standard types for
intuitionistic linear logic.  We have a constant $[[UnitT]]$, tensor
product $[[X (*) Y]]$, and linear implication $[[X -o Y]]$, but just
as in LNL logic we also have a type $[[Gf A]]$ where $[[A]]$ is an
$\cat{L}$-type; that is, a type from the non-commutative side
corresponding to the right-adjoint functor between $\cat{L}$ and
$\cat{C}$. This functor can be used to import types and terms from the
non-commutative side into the commutative side.  Now $\cat{C}$-typing
judgments are denoted by $[[P |-c t : X]]$ where $[[P]]$ is a sequence
of pairs of variables and their types, denoted by $[[x : X]]$, $[[t]]$
is a $\cat{C}$-term, and $[[X]]$ is a $\cat{C}$-type.  The
$\cat{C}$-terms are all standard, but $[[Gf s]]$ corresponds to the
morphism part of the right-adjoint of the adjunction between both
logics, and $[[ex t1 , t2 with x1 , x2 in t3]]$ is the introduction
form for the structural rule exchange.

The non-commutative side is a bit more interesting than the
commutative side just introduced.  The $\cat{L}$-typing judgment has
the form $[[G |-l s : A]]$ where $[[G]]$ is now a $\cat{L}$-context,
denoted by $[[G]]$ or $[[D]]$. These contexts are ordered sequences of
pairs of free variables with their types from \emph{both} sides
denoted by $[[x : B]]$ and $[[x : X]]$ respectively. Finally, the term
$[[s]]$ is a $\cat{L}$-term, and $[[A]]$ is a $\cat{L}$-type.  Given
two typing contexts $[[G]]$ and $[[D]]$ we denote their concatenation
by $[[G;D]]$; we use a semicolon here to emphasize the fact that the
contexts are ordered.

The context consisting of hypotheses from both sides goes back to
Benton~\cite{Benton:1994} and is a property unique to adjoint logics
such as Benton's LNL logic and CNC logic.  This is also a very useful
property because it allows one to make use of both sides within the
Lambek calculus without the need to annotate every formula with a
modality.

The reader familiar with LNL logic will notice that our typing
judgment, $[[G |-l s : A]]$, differs from Benton's. His is of the form
$\Gamma;\Delta \vdash t : A$, where $\Gamma$ contains non-linear
formulas, and $\Delta$ contains linear formulas.  Just as Benton
remarks, the splitting of his contexts was a presentational device.
One should view his contexts as merged, and hence, linear formulas
were fully mixed with non-linear formulas.  Now why did we not use
this presentational device?  Because, when contexts from LNL logic
become out of order Benton could use the exchange rule to put them
back in order again, but we no longer have general exchange. Thus, we
are not able to keep the context organized in this way.

The syntax for $\cat{L}$-types are of the typical form for the Lambek
Calculus.  We have an unit type $[[UnitS]]$, a non-commutative tensor
product $[[A (>) B]]$, right implication $[[A -> B]]$, and left
implication $[[B <- A]]$.  $\cat{L}$-terms correspond to introduction
and elimination forms for each of the previous types.  For example,
$[[s1 (>) s2]]$ introduces a tensor, and $[[let s1 : A (>) B be x (>)
    y in s2]]$ eliminates a tensor.

The typing rules for CNC logic can be found in
Figure~\ref{fig:CNC-typing-rules}.
\begin{figure}
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
      \begin{mathpar}
      \NDdruleTXXid{} \and
      \NDdruleTXXunitI{} \and
      \NDdruleTXXunitE{} \and
      \NDdruleTXXtenI{} \and
      \NDdruleTXXtenE{} \and
      \NDdruleTXXimpI{} \and
      \NDdruleTXXimpE{} \and
      \NDdruleTXXGI{} \and
      \NDdruleTXXbeta{} \and
      \NDdruleTXXcut{}      
      \end{mathpar}
      \\
      \\
      \hline
      \\[5px]
    \begin{mathpar}
      \NDdruleSXXid{} \and
      \NDdruleSXXunitI{} \and
      \NDdruleSXXunitETwo{} \and
      \NDdruleSXXunitEOne{} \and
      \NDdruleSXXtenI{} \and
      \NDdruleSXXtenETwo{} \and
      \NDdruleSXXtenEOne{} \and
      \NDdruleSXXimprI{} \and
      \NDdruleSXXimprE{} \and
      \NDdruleSXXimplI{} \and
      \NDdruleSXXimplE{} \and
      \NDdruleSXXFI{} \and
      \NDdruleSXXFE{} \and
      \NDdruleSXXGE{} \and
      \NDdruleSXXbeta{} \and
      \NDdruleSXXcutTwo{} \and
      \NDdruleSXXcutOne{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{Typing Rules for CNC Logic}
  \label{fig:CNC-typing-rules}
\end{figure}
We split the figure in two: the top of the figure are the rules of
intuitionistic linear logic whose judgment is the $\mathcal{C}$-typing
judgment denoted by $[[P |-c t : X]]$, and the bottom of the figure
are the rules for the mixed commutative/non-commutative Lambek
calculus whose judgment is the $\mathcal{L}$-judgment denoted by $[[G
    |-l s : A]]$, but the two halves are connected via the functor
rules $\NDdruleTXXGIName{}$, $\NDdruleSXXGEName{}$,
$\NDdruleSXXFIName{}$, and $\NDdruleSXXFEName{}$.  Just as in LNL
logic, the fact that the context $[[G]]$ on the $\mathcal{L}$ side of
the logic is mixed results in this side having additional elimination
rules, because the type being eliminated is constructed on the
$\mathcal{C}$ side of the logic; for example, the rules
$\NDdruleSXXunitEOneName{}$, $\NDdruleSXXtenEOneName{}$, and
$\NDdruleSXXcutOneName{}$ are additional mixed rules.

The one step $\beta$-reduction rules are listed in
Figure~\ref{fig:CNC-beta-reductions}. Similarly to the typing rules,
the figure is split in two: the top lists the rules of the
intuitionistic linear logic, and the bottom are those of the mixed
commutative/non-commutative Lambek calculus. 
\renewcommand{\NDdruleTbetaXXletUName}{}
\renewcommand{\NDdruleTbetaXXletTName}{}
\renewcommand{\NDdruleTbetaXXlamName}{}
\renewcommand{\NDdruleTbetaXXappOneName}{}
\renewcommand{\NDdruleTbetaXXappTwoName}{}
\renewcommand{\NDdruleTbetaXXappLetName}{}
\renewcommand{\NDdruleTbetaXXletLetName}{}
\renewcommand{\NDdruleTbetaXXletAppName}{}
\renewcommand{\NDdruleSbetaXXletUOneName}{}
\renewcommand{\NDdruleSbetaXXletTOneName}{}
\renewcommand{\NDdruleSbetaXXletTTwoName}{}
\renewcommand{\NDdruleSbetaXXletFName}{}
\renewcommand{\NDdruleSbetaXXlamLName}{}
\renewcommand{\NDdruleSbetaXXlamRName}{}
\renewcommand{\NDdruleSbetaXXapplOneName}{}
\renewcommand{\NDdruleSbetaXXapplTwoName}{}
\renewcommand{\NDdruleSbetaXXapprOneName}{}
\renewcommand{\NDdruleSbetaXXapprTwoName}{}
\renewcommand{\NDdruleSbetaXXderelictName}{}
\renewcommand{\NDdruleSbetaXXapplLetName}{}
\renewcommand{\NDdruleSbetaXXapprLetName}{}
\renewcommand{\NDdruleSbetaXXletLetName}{}
\renewcommand{\NDdruleSbetaXXletApplName}{}
\renewcommand{\NDdruleSbetaXXletApprName}{}
\renewcommand{\NDdruleTcomXXunitEXXunitEName}{}
\renewcommand{\NDdruleTcomXXunitEXXtenEName}{}
\renewcommand{\NDdruleTcomXXunitEXXimpEName}{}
\renewcommand{\NDdruleTcomXXtenEXXunitEName}{}
\renewcommand{\NDdruleTcomXXtenEXXtenEName}{}
\renewcommand{\NDdruleTcomXXtenEXXimpEName}{}
\renewcommand{\NDdruleTcomXXimpEXXunitEName}{}
\renewcommand{\NDdruleScomXXunitEXXunitEName}{}
\renewcommand{\NDdruleScomXXunitETwoXXunitEName}{}
\renewcommand{\NDdruleScomXXunitEXXimprEName}{}
\renewcommand{\NDdruleScomXXunitETwoXXimprEName}{}
\renewcommand{\NDdruleScomXXunitEXXFEName}{}
\renewcommand{\NDdruleScomXXunitETwoXXFEName}{}
\renewcommand{\NDdruleScomXXtenEXXunitEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXunitEName}{}
\renewcommand{\NDdruleScomXXtenEXXtenEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXtenEName}{}
\renewcommand{\NDdruleScomXXtenEXXimprEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXimprEName}{}
\renewcommand{\NDdruleScomXXtenEXXimplEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXimplEName}{}
\renewcommand{\NDdruleScomXXtenEXXFEName}{}
\renewcommand{\NDdruleScomXXtenETwoXXFEName}{}
\renewcommand{\NDdruleScomXXFEXXunitEName}{}
\renewcommand{\NDdruleScomXXFEXXtenEName}{}
\renewcommand{\NDdruleScomXXFEXXimprEName}{}
\renewcommand{\NDdruleScomXXFEXXimplEName}{}
\renewcommand{\NDdruleScomXXFEXXFEName}{}
\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
      \begin{mathpar}
      \NDdruleTbetaXXletU{} \and
      \NDdruleTbetaXXletT{} \and
      \NDdruleTbetaXXlam{}
      \end{mathpar}
      \\
      \\
      \hline
      \\
    \begin{mathpar}
      \NDdruleSbetaXXletUOne{} \and
      \NDdruleSbetaXXletTOne{} \and
      \NDdruleSbetaXXletTTwo{} \and
      \NDdruleSbetaXXletF{} \and
      \NDdruleSbetaXXlamL{} \and
      \NDdruleSbetaXXlamR{} \and
      \NDdruleSbetaXXderelict{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{$\beta$-reductions for CNC Logic}
  \label{fig:CNC-beta-reductions}
\end{figure}

The commuting conversions can be found in
Figures~\ref{fig:CNC-commutating-conversions-intuitionistic}-\ref{fig:CNC-commutating-conversions-both}. We
divide the rules into three parts due to the length. The first part,
Figure~\ref{fig:CNC-commutating-conversions-intuitionistic}, includes
the rules for the intuitionistic linear logic. The second,
Figure~\ref{fig:CNC-commutating-conversions-mixed}, includes the rules
for the commutative/non-commutative Lambek calculus. The third,
Figure~\ref{fig:CNC-commutating-conversions-both}, includes the mixed
rules $\NDdruleSXXunitEOneName{}$ and $\NDdruleSXXtenEOneName{}$.

\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
    \begin{mathpar}
      \NDdruleTcomXXunitEXXunitE{} \and
      \NDdruleTcomXXunitEXXtenE{} \and
      \NDdruleTcomXXunitEXXimpE{} \and
      \NDdruleTcomXXtenEXXunitE{} \and
      \NDdruleTcomXXtenEXXtenE{} \and
      \NDdruleTcomXXtenEXXimpE{} \and
      \NDdruleTcomXXimpEXXunitE{}
    \end{mathpar}
    \\
    \\
    \hline
  \end{tabular}  
  \caption{Commuting Conversions: Intuitionistic Linear Logic}
  \label{fig:CNC-commutating-conversions-intuitionistic}
\end{figure}
\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
    \begin{mathpar}
      \NDdruleScomXXunitEXXunitE{} \and
      \NDdruleScomXXunitEXXimprE{} \and
      \NDdruleScomXXunitEXXFE{} \and
      \NDdruleScomXXtenEXXunitE{} \and
      \NDdruleScomXXtenEXXtenE{} \and
      \NDdruleScomXXtenEXXimprE{} \and
      \NDdruleScomXXtenEXXimplE{} \and
      \NDdruleScomXXtenEXXFE{} \and
      \NDdruleScomXXFEXXunitE{} \and
      \NDdruleScomXXFEXXtenE{} \and
      \NDdruleScomXXFEXXimprE{} \and
      \NDdruleScomXXFEXXimplE{} \and
      \NDdruleScomXXFEXXFE{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{Commuting Conversions: Commutative/Non-commutative Lambek Calculus}
  \label{fig:CNC-commutating-conversions-mixed}
\end{figure}
\begin{figure}[!h]
  \footnotesize
  \begin{tabular}{|c|}
    \hline\\
    \begin{mathpar}
      \NDdruleScomXXunitETwoXXunitE{} \and
      \NDdruleScomXXunitETwoXXimprE{} \and
      \NDdruleScomXXunitETwoXXFE{} \and
      \NDdruleScomXXtenETwoXXunitE{} \and
      \NDdruleScomXXtenETwoXXtenE{} \and
      \NDdruleScomXXtenETwoXXimprE{} \and
      \NDdruleScomXXtenETwoXXimplE{} \and
      \NDdruleScomXXtenETwoXXFE{}
    \end{mathpar}\\\\
    \hline
  \end{tabular}  
  \caption{Commuting Conversions: Mixed Rules}
  \label{fig:CNC-commutating-conversions-both}
\end{figure}

\textbf{Additional Results.} The following subsection shows the
reduction rules for CNC Logic. In addition to the results given in this
paper we also have defined a sequent calculus for CNC logic, proved
cut elimination, and proved the the sequent calculus formalization is
equivalent to the natural deduction formalization given here.
Furthermore, we proved strong normalization of CNC logic via a
translation to LNL logic.  We omit these results due to space.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: main.tex
%%% End:

>>>>

Section for sequent calculus

\begin{mathpar}
\end{mathpar}
